SMT-COMP 2023\\ 18th International Satisfiability Modulo Theory Competition

### 2023-07-06 2023/slides/presresults/slides.tex
revert compute_from_yaml
Last addition in slides

\medskip
\pause
  \emph{This year} the sat/unsat results from sound solvers in SQ were used to
  include benchmarks on the MV, UC and PE tracks.

@@

@@

  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
\item cvc5
\vitem Q3B
\vitem Q3B-pBDD
\vitem STP
\vitem UltimateIntBlastingWrapper+SMTInterpol
\vitem z3-alpha
\vitem Z3-Noodler
\vitem Z3-Owl
    \end{itemize}
  \end{frame}

@@

\begin{frame}{Plans for SMT-COMP 2023}
  \begin{itemize}
    \item "Revelations are found in clouds” --- Serge King
    \item MV: Algebraic number non experimental
    \item MV: partial function more discussion needed
    \item MV: array theory more discussion needed
  \end{itemize}
\end{frame}

>>>>

\medskip
\pause
  \emph{As last year} the sat/unsat results from sound solvers in SQ were used to
  include benchmarks on the MV, UC and PE tracks.

@@

\myincludepdf{slides-cvc5.pdf}

@@

  \begin{frame}
    \frametitle{Other participants}
    \begin{itemize}
\item Q3B
\vitem Q3B-pBDD
\vitem STP
\vitem UltimateIntBlastingWrapper+SMTInterpol
\vitem z3-alpha
\vitem Z3-Noodler
\vitem Z3-Owl
    \end{itemize}
  \end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Plans for SMT-COMP 2023}
  \begin{itemize}
    \item "Revelations are found in clouds” --- Serge King
    \item MV: Algebraic number $\implies$ non experimental
\begin{verbatim}
(root-of-with-ordering (coeffs p_0 p_1 ... p_n) i)

(root-of-with-interval  (coeffs p_0 p_1 ... p_n) min max)
(root-of-with-enclosure (coeffs p_0 p_1 ... p_n) min max)
\end{verbatim}
    Thanks for the solvers that implemented one of them!
    \item MV: partial function more discussion needed
    \item MV: array theory more discussion needed
  \end{itemize}
\end{frame}
